---
title: "Solution Exam 1"
format: 
  html:
    self-contained: true

execute:
  message: false
  warning: false
---

# Exam 1 Sec 21

```{r}
library(tidyverse)
survey <- read_rds("data/survey.rds")
```

## Concept

- Q1) b TRUE 
- Q2) d variables 
- Q3) a faceted histogram 
- Q4a) b scatterplot 
- Q4b) e stacked barplots 
- Q5) a 
- Q6a) b decrease 
- Q6b) c stay the same 
- Q7a) d neither A nor B 
- Q7b) a meansure of center 
- Q7c) b measure of variation 
- Q8a) c mutate 
- Q8b) e filter 
- Q8c) g summarize 
- Q9) a

## Application 1

```{r}
ggplot(survey, 
       aes(x = num_followers, 
           y = height_inches,
           color = personality)) +
  geom_point()
```

No association
Should not be surprising (but as long as they defend opinion)

## Application 2

```{r}
survey %>% 
  filter(school_year != "First year") %>% 
  group_by(campus_housing) %>% 
  summarize(mean = mean(num_party, na.rm= TRUE)) %>% 
  arrange(mean)
```

## Application 3

```{r}
ggplot(data = survey, aes(x=salary)) +
  geom_histogram(bins = 18, color = "white")
```

```{r}
#any wrangling here will suffice so long as it works
```

- describe center in some way (if wrangling is not right can approximate based on picture instead)
- describe spread in some way (if wrangling is not right can approximate based on picture instead)
- right skewed
- could defend unimodal or bimodal depending on graph
