---
title: "Solution Exam 1"
subtitle: "Version B"
format: 
  html:
    self-contained: true

execute:
  message: false
  warning: false
---

# Exam 1 Version B

```{r}
library(tidyverse)
survey <- read_rds("data/survey.rds") %>%
  # remove impossible data and extreme outliers
  mutate(
    followers_insta = ifelse(followers_insta == 0, NA,
                           ifelse(followers_insta > 4000, NA,
                                  followers_insta)),
    followers_tiktok = ifelse(followers_tiktok == 0, NA,
                           ifelse(followers_tiktok > 4000, NA,
                                  followers_tiktok)),
    height_inches = ifelse(height_inches < 42, NA,
                           ifelse(height_inches > 84, NA,
                                  height_inches)),
    mother_height = ifelse(mother_height < 42, NA,
                           ifelse(mother_height > 84, NA,
                                  mother_height)),
    father_height = ifelse(father_height < 42, NA,
                           ifelse(father_height > 84, NA,
                                  father_height)),
    salary = ifelse(salary < 500000, salary, NA)
    ) %>% 
  select(quarter, gender_ident, school_year, num_party, procrastinator, 
          height_inches, happy, campus_housing, smoke_weed,
         followers_insta, followers_tiktok, salary)
```

## Concept

- Q1) FALSE
- Q2) variables 
- Q3) faceted histogram 
- Q4) barplot
- Q5) scatterplot 
- Q6) stacked barplots 
- Q7) position = `dodge`
- Q8) The distribution is skewed left and the mean is less than the median.
- Q9) increase
- Q10) stay the same 
- Q11) Measure of Centrality/Center
- Q12) Neither a measure of Centrality and Variability
- Q13) Measure of Variability/Spread
- Q14) arrange()
- Q15) select()
- Q16) group_by()
- Q17) dplyr
- Q18) geom_*()
- Q19) +
- Q20) some data %>% filter() %>% group_by() %>% summarize()

## Application 1

```{r}
ggplot(survey, 
       aes(x = followers_insta, 
           y = followers_tiktok,
           color = procrastinator)) +
  geom_point()
```

Weak positive
Should not be surprising (but as long as they defend opinion)

## Application 2

```{r}
survey %>% 
  filter(school_year != "First year") %>% 
  group_by(campus_housing) %>% 
  summarize(mean = mean(num_party, na.rm= TRUE)) %>% 
  arrange(mean)
```


## Application 2

```{r}
survey %>% 
  mutate(height_feet = height_inches/12) %>% 
  select(quarter, height_inches, height_feet)
```

## Application 4

```{r}
survey_party <- survey %>% 
  filter(!is.na(smoke_weed), happy != "Don't know")

ggplot(data = survey_party, aes(x=happy, fill = smoke_weed)) +
  geom_bar(position = 'fill')
```


- any explanation as long as it makes sense
