---
title: "Solution Exam 3"
format: 
  html:
    self-contained: true

execute:
  message: false
  warning: false
---

# Exam 3

```{r}
library(tidyverse)
survey <- read_rds("data/survey.rds")
```


## Concept

- Q1) B
- Q2) C
- Q3) A 
- Q4) C
- Q5) C 
- Q6) D
- Q7) E
- Q8) B
- Q9) B
- Q10) B
- Q11) A
- Q12) B
- Q13) A
- Q14) B
- Q15) B
- Q16) B
- Q17) C
- Q18) B

## Application 1

```{r}
t.test(x = survey$gpa_nu, conf.level = 0.95)
```

We are 95% confident that the average gpa for **students who take STAT 202** at NU is between xx and xx.

## Application 2

```{r}
survey %>% 
  count(happy)

prop.test(x = 93, n = 547, conf.level = 0.98, correct = FALSE)
```

We are 98% confident that the proportion of **students who take STAT 202** at NU that are very happy is between xx and xx.


## Application 3

```{r}
extrovert <- survey %>% 
  filter(personality == "Extrovert")

introvert <- survey %>% 
  filter(personality == "Introvert")

t.test(x = extrovert$num_followers, y = introvert$num_followers)
#might have added on conf.level = 0.9
```

Sample interpretation:

Assuming the **average number of Instagram followers is the same** between extroverts and introverts for **students who take STAT 202** at NU, there is a xx% chance of seeing data as extreme as ours. At the alpha = 0.1 significance level, we **reject the null hypothesis**. There is a difference between average number of followers and since our sample estimate of extroverts is higher than introverts, **extroverts have more followers**.