---
title: "Solution Exam 3"
subtitle: "Version B"
format: 
  html:
    self-contained: true

execute:
  message: false
  warning: false
---

# Exam 3

```{r}
#| echo: false
library(tidyverse)
survey <- read_rds("data/survey.rds") %>% 
  mutate(
    followers_insta = ifelse(followers_insta == 0, NA,
                           ifelse(followers_insta > 4000, NA,
                                  followers_insta)),
    followers_tiktok = ifelse(followers_tiktok == 0, NA,
                           ifelse(followers_tiktok > 4000, NA,
                                  followers_tiktok)),
    height_inches = ifelse(height_inches < 42, NA,
                           ifelse(height_inches > 84, NA,
                                  height_inches)),
    mother_height = ifelse(mother_height < 42, NA,
                           ifelse(mother_height > 84, NA,
                                  mother_height)),
    father_height = ifelse(father_height < 42, NA,
                           ifelse(father_height > 84, NA,
                                  father_height)),
    salary = ifelse(salary < 500000, salary, NA),
    gpa_nu = ifelse(gpa_nu > 4, NA, gpa_nu),
    gpa_hs = ifelse(gpa_hs > 5, NA, gpa_hs),
    exercise = ifelse(exercise > 2500, NA, exercise)
    ) %>% 
  select(quarter, gender_ident, school_year, num_party, fav_drink, personality, 
          campus_housing, happy, gpa_hs, gpa_nu,  followers_insta,
         followers_tiktok, brain_type, exercise)
```


## Concept

- Q1) Plot b
- Q2) Plot c  
- Q3) Plot a
- Q4) the average number of times that a college student checks their phone is between 85 and 135 times per day
- Q5) There is a 6% chance our interval does not contain the population parameter
- Q6) increase the standard error
- Q7) standard error becomes larger
- Q8) We expect 90 students to decide that there is no difference
- Q9) the person is told they have diabetes and the truth is they do not have diabetes
- Q10) the decision depends on the significance level they set before conducting the experiment
- Q11) TRUE
- Q12) FALSE
- Q13) FALSE
- Q14) TRUE
- Q15) FALSE
- Q16) FALSE
- Q17) c
- Q18) Reject the null, there is statistically significant evidence that star wars is better than lord of the rings.

## Application 1

```{r}
t.test(x = survey$exercise, conf.level = 0.99)
```

We are 99% confident that the average weekly minutes of exercise for **students who take STAT 202** at NU is between xx and xx.

## Application 2

```{r}
survey %>% 
  count(school_year)

prop.test(x = 370, n = 677, conf.level = 0.90, correct = FALSE)
```

We are 90% confident that the proportion of **students who take STAT 202** at NU that are First years is between xx and xx.


## Application 3

```{r}
happy <- survey %>% 
  filter(happy == "Very happy")

sad <- survey %>% 
  filter(happy == "Not too happy")

t.test(x = happy$followers_insta, y = sad$followers_insta)
#might have added on conf.level = 0.97
#if did not add conf.level that is okay
#if added on any conf.level that is NOT 0.97 error! Deduct!
```

Sample interpretation:

Assuming the **average number of Instagram followers is the same** between Very happy and Not too happy **students who take STAT 202** at NU, there is a xx% chance of seeing data as extreme as ours. At the alpha = 0.03 significance level, we **reject the null hypothesis**. There is a difference between average number of followers and since our sample estimate of extroverts is higher than introverts, this implies that **Very happy students have more followers**.