---
title: "Solution Exam 3"
format: 
  html:
    self-contained: true

execute:
  message: false
  warning: false
---

# Exam 3

```{r}
library(tidyverse)
survey <- read_rds("data/survey.rds")
```


## Concept

- Q1a) C
- Q1b) D  
- Q1c) A 
- Q1d) B
- Q2) the average of 50 customer's meal price
- Q3) the average number of exclusive relationships that college students have been in is between 2.7 and 3.7
- Q4) There is a 2% chance our interval does not contain the population parameter
- Q5) increase the sample size
- Q6) a p-value is the probability of observing an estimate as extreme as our sample estimate if the null hypothesis is true
- Q7) p-value for a hypothesis test becomes larger
- Q8) We expect 9 students to decide that there is a non-zero difference
- Q9) the person is told they have cancer and the truth is they do not have cancer
- Q10) the decision depends on the significance level they set before conducting the experiment
- Q11) FALSE
- Q12) TRUE
- Q13) FALSE
- Q14) FALSE
- Q15) FALSE
- Q16) c
- Q17) Fail to reject the null, the teacher is correct that at least 90% of students studied.

## Application 1

```{r}
t.test(x = survey$gpa_nu, conf.level = 0.9)
```

We are 90% confident that the average gpa for **students who take STAT 202** at NU is between xx and xx.

## Application 2

```{r}
survey %>% 
  count(happy)

prop.test(x = 80, n = 682, conf.level = 0.98, correct = FALSE)
```

We are 98% confident that the proportion of **students who take STAT 202** at NU that are very happy is between xx and xx.


## Application 3

```{r}
extrovert <- survey %>% 
  filter(personality == "Extrovert")

introvert <- survey %>% 
  filter(personality == "Introvert")

t.test(x = extrovert$followers_insta, y = introvert$followers_insta)
#might have added on conf.level = 0.99
#if did not add conf.level that is okay
#if added on any conf.level that is NOT 0.99 error! Deduct!
```

Sample interpretation:

Assuming the **average number of Instagram followers is the same** between extroverts and introverts for **students who take STAT 202** at NU, there is a xx% chance of seeing data as extreme as ours. At the alpha = 0.01 significance level, we **reject the null hypothesis**. There is a difference between average number of followers and since our sample estimate of extroverts is higher than introverts, **extroverts have more followers**.