---
title: "Solution Exam 2"
format: 
  html:
    self-contained: true

execute:
  message: false
  warning: false
---

# Exam 2 Sec 20

```{r}
library(tidyverse)
survey <- read_rds("data/survey1.rds")

survey_f <- survey %>% 
  filter(gender_ident == "Female")
```

## Concept

- Q1) b) Between -1 and 0
- Q2) d) 0.30
- Q3) a) over-estimate 
- Q4) d) NV
- Q5) c) intercept for males 
- Q6) f) offset in slope of age for females
- Q7) a)
- Q8) b) no causal conclusions, correlation statement generalized to the University
- Q9) d) stratified sampling
- Q10) a) $\\bar{x}$
- Q11) b) only our sample
- Q12) b) a variable that affects the outcome being measured as well as, or instead of, the independent variable
- Q13) c) No, while the stratums are homogenous (within each stratum people share a characteristic) the upper class is being overrepresented in the sample because a small percent of the true population belongs to the upper class.
- Q14) 30 and 36
- Q15) b) pnorm(q = 1.25, lower.tail = FALSE) 
- Q16) a) qnorm(p = 0.25, mean = 3, sd = 0.5)

## Application 1

**Part 1**
```{r}
survey_f %>% 
  filter(!is.na(height_inches), !is.na(mother_height)) %>% 
  select(height_inches, mother_height) %>% 
  cor()
```
MANY ways to solve this.
Should have **cor =  0.539**

-1 cor should not be NA
-1 wrong cor

**Part 2**

geom_smooth(method = "lm")

**Part 3**
```{r}
model <- lm(height_inches ~ mother_height, data = survey_f)
summary(model)
```

**Part 4**


## Application 2

```{r}
model2 <- lm(num_party ~ fav_drink, data = survey_f)

summary(model2)
```
Q1) d) wine
Q2) b) don't_drink
Q3) c) hard_liquor